Automatic Bicycle Balance Assistance Reduces Probability of Falling at Low Speeds When Subjected to Handlebar Perturbations\\Version 2.dev

### 2024-09-26 main.tex
Minor wording.

Turning the balance assist system on significantly \((p<0.05)\) reduces the
odds that a perturbation results in a fall while cycling at a speed of
6~\si{\kph}. Figure~\ref{fig:probability-6kph} visualizes the probability of
falling as a function of the mean and centered angular impulse per participant
for the balance assist state on and off while keeping all other explanatory
factors at their centered mean values. This figure is created by setting all
explanatory variables to their mean and calculating the probability from
Equation~\ref{eq:log-regress} for only change in angular impulse given the
estimates in Table~\ref{tab:freq-coefs-6}. The table indicates that the balance
assist system halves (0.53) the odds that a perturbation results in a fall.
This figure shows that for relatively large impulses the probability to fall is
unity for both states of balance assist on and off. And for relatively small
impulses the probability to fall is null for both states. But for impulses in
the magnitude region (about -1 to 0.5 STD), i.e. around the mean-centered
perturbation resistance threshold, the probability of falling is significantly
lowered with the balance assist system on. The skewness of the probability
curves arrives from the interaction effects. Figure~\ref{fig:probability-10kph}
shows the same result for the 10~\si{\kph} trials which has a similar trend of
reducing the probability to fall with the balance assist system turned on, but
the effect is not significant.
%
\begin{figure}
  \centering
  \subcaptionbox{Fall probability for the 6~\si{\kph} trials.
    \label{fig:probability-6kph}}{
    \includegraphics[width=80mm]{figures/predicted_fall_probability_6kmh.png}
  }
  \subcaptionbox{Fall probability for the 10~\si{\kph} trials.
    \label{fig:probability-10kph}}{
    \includegraphics[width=80mm]{figures/predicted_fall_probability_10kmh.png}
  }
  \caption{Comparison of predicted fall probability for balance assist on
    (solid) or off (dashed) when all other predictor variables are fixed at zero,
    except for the interaction effect between the balance assist and the
    angular impulse. The abscissa is the standard deviation around the mean
    (all perturbations), centered per participant.}
  \label{fig:probability}
\end{figure}

>>>>

Turning the balance assist system on significantly \((p<0.05)\) reduces the
odds that a perturbation results in a fall while cycling at a speed of
6~\si{\kph}. Figure~\ref{fig:probability-6kph} visualizes the probability of
falling as a function of the mean and centered angular impulse per participant
for the balance assist state on and off while keeping all other explanatory
factors at their centered mean values. This figure is created by setting all
explanatory variables to their mean and calculating the probability from
Equation~\ref{eq:log-regress} for only change in angular impulse given the
estimates in Table~\ref{tab:freq-coefs-6}. The table indicates that the balance
assist system halves (0.53) the odds that a perturbation results in a fall.
This figure shows that for relatively large impulses the probability to fall is
unity for both states of balance assist on and off. And for relatively small
impulses the probability to fall is null for both states. But for impulses in
the magnitude region (about -1 to 0.5 STD), i.e. around the mean-centered
perturbation resistance threshold, the probability of falling is significantly
lowered with the balance assist system on. The skewness of the probability
curves arrives from the interaction effects. Figure~\ref{fig:probability-10kph}
shows the same result for the 10~\si{\kph} trials which has a similar trend of
reducing the probability to fall with the balance assist system turned on, but
the effect is not significant.
%
\begin{figure}
  \centering
  \subcaptionbox{Fall probability for the 6~\si{\kph} trials.
    \label{fig:probability-6kph}}{
    \includegraphics[width=80mm]{figures/predicted_fall_probability_6kmh.png}
  }
  \subcaptionbox{Fall probability for the 10~\si{\kph} trials.
    \label{fig:probability-10kph}}{
    \includegraphics[width=80mm]{figures/predicted_fall_probability_10kmh.png}
  }
  \caption{Comparison of predicted fall probability for balance assist on
    (solid) or off (dashed) when all other predictor variables are set to zero,
    except for the interaction effect between the balance assist and the
    angular impulse. The abscissa is the standard deviation around the mean
    (all perturbations), centered per participant.}
  \label{fig:probability}
\end{figure}
